Using the allocation scoring rule to evaluate short-term COVID-19 hospitalization forecasts during the 2021-2022 Omicron wave

### 2023-09-01 alloscore_manuscript/application.Rnw
changes to make project root dir the knitr location and fixing one typo that was making latex stop.

theme_set(theme_bw())
@

@@

Models show differing levels of correlation between their allocation scores and MWIS values (Figure XX).
Here are some examples of the different patterns observed:
\begin{itemize}
\item positive association between allocation score and MWIS ranks: \texttt{Karlen-pypm} and \texttt{USC-SI_kJalpha} models
\item consistently strong MWIS ranks, highly variable allocation score ranks, no clear association: \texttt{JHUAPL-SLPHospEns} and \texttt{CU-select}
\item consistently strong ranks for both metrics, no clear association: \texttt{COVIDhub-ensemble}
\end{itemize}
Additionally, the \texttt{COVIDhub-baseline} model, which predicts a flat line from the most recent observation with uncertainty bounds based on a random walk, had the highest rank for allocation score in six weeks, more than any other model except the \texttt{COVIDhub-ensemble} which also had six.

>>>>

theme_set(theme_bw())

## necessary to have project root as wd, to override document directory
knitr::opts_knit$set(root.dir = '../')
@

@@

Models show differing levels of correlation between their allocation scores and MWIS values (Figure XX).
Here are some examples of the different patterns observed:
\begin{itemize}
\item positive association between allocation score and MWIS ranks: \texttt{Karlen-pypm} and \texttt{USC-SI\_kJalpha} models
\item consistently strong MWIS ranks, highly variable allocation score ranks, no clear association: \texttt{JHUAPL-SLPHospEns} and \texttt{CU-select}
\item consistently strong ranks for both metrics, no clear association: \texttt{COVIDhub-ensemble}
\end{itemize}
Additionally, the \texttt{COVIDhub-baseline} model, which predicts a flat line from the most recent observation with uncertainty bounds based on a random walk, had the highest rank for allocation score in six weeks, more than any other model except the \texttt{COVIDhub-ensemble} which also had six.
